### 2011-11-07 doc/pldi2012/code_ex.tex

  CircuitPiece<c.r_all_nodes,c.r_all_wires> pieces[MAX_PIECES];
  for(i = 0; i #$<$# MAX_PIECES; i++) 
    pieces[i] #$\gets$# { rn_pvt = p_pvt_nodes[i], rn_shr = p_shr_nodes[i],
                            rn_ghost = p_ghost_nodes[i], rw_pvt = p_wires[i] };

>>>>

  CircuitPiece<c.r_all_nodes,c.r_all_wires> pieces[MAX_PIECES];
  for(i = 0; i #$<$# MAX_PIECES; i++) 
    pieces[i] #$\gets$# region_cast<CircuitPiece<c.r_all_nodes,c.r_all_wires> >
                          { rn_pvt = p_pvt_nodes[i], rn_shr = p_shr_nodes[i],
                             rn_ghost = p_ghost_nodes[i], rw_pvt = p_wires[i] };

### 2011-11-07 doc/pldi2012/type_system.tex
Fixing a few small typos

As mentioned above, region privileges are not stored in packed types;
instead, privileges are passed through the task call tree.  This is a key
property of the type system, and is what allows the runtime to 
track which regions are in use by which tasks and to make distributed
scheduling decisions.
Each subtask must obtain its privileges from
the task that calls it.  For example, in Listing~\ref{lst:code_ex},
the task {\tt calc\_new\_currents} requires regions {\tt piece.rw\_pvt} with {\tt RW} privileges
and {\tt piece.rn\_pvt} and {\tt piece.rn\_ghost} with {\tt RO} (read-only) privileges.  Because the calling task has {\tt RW} privileges on the parent regions of these
region arguments, the type checker is able to confirm that the subtask can execute with the needed privileges.

@@

Due the the inability for a packed region relationship to hold privileges, any
useful region relationship will leave at least one region free (i.e. unquantified) and include constraints that relate the quantified region(s) to the free one(s).  As long as a task holds a privilege for the region that is kept free, the
region relationship can be unpacked and used.

>>>>

As mentioned above, region privileges are not stored in packed types;
instead, privileges are passed through the task call tree.  This is a key
property of the type system, and is what allows the runtime to 
track which regions are in use by which tasks and to make distributed
scheduling decisions.
Each subtask must obtain its privileges from
the task that calls it.  For example, in Listing~\ref{lst:code_ex},
the task {\tt calc\_new\_currents} requires regions {\tt piece.rw\_pvt} with {\tt RW} privileges
and {\tt piece.rn\_pvt} and {\tt piece.rn\_ghost} with {\tt RO} (read-only) privileges.  Because the calling task has {\tt RW} privileges on the parent regions of these
region arguments, the type checker can confirm that the subtask can execute with the needed privileges.

@@

Due to the inability for a packed region relationship to hold privileges, any
useful region relationship will leave at least one region free (i.e. unquantified) and include constraints that relate the quantified region(s) to the free one(s).  As long as a task holds a privilege for the region that is kept free, the
region relationship can be unpacked and used.
